Robust receding horizon control for linear systems with state and input dependent disturbances

### 2015-06-30 example.tex
Modified example.

\section{Example}\label{sec:example}
In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}. The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
on the coil, $y$ the vertical distance to the coil (Fig.~\ref{fig:levitating:ball}). We assume that the current~$i$ is directly specified by the controller, thus neglecting the inductive dynamics of the coil. %Figure~\ref{fig:levitating:ball} illustrates the setup.
Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
on the state and control input. For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.

>>>>

\section{Example}\label{sec:example}
In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}. The dynamics of the nonlinear system are given by $m\ddot y = m g - c i^2/y^2$,
where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
on the coil, $y$ the vertical distance to the coil (Fig.~\ref{fig:levitating:ball}). We assume that the current~$i$ is directly specified by the controller, thus neglecting the inductive dynamics of the coil. %Figure~\ref{fig:levitating:ball} illustrates the setup.
Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
on the state and control input. For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.
